Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
table 2

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results}
We used various Reducer Nodes , simulation code and optimization algorithms in our experiments.
A summary is listed in Table~\ref{tab:built-in}
\begin{table}
\centering %why
\begin{tabular}{|p{2.5cm}|p{2.5cm}|p{2.5cm}|}
\hline 
Reducer Node & simulator & optimization\\
\hline 
Geometry Node & optics & \multirow{4}{*}{Error Diffusion, SPSA}\\
 InputMesh, Stratum, Column&\\ \cline{1-2}
Material Node & deformation  \\
Constant, Layered,
QuadLayer, SubdivisionSufrace& \\
\hline 
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table}
\subsection{Print Material Characterization and Measurement}
\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. 
In this example, we
tried to make the material as light as possible.

>>>>

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results}
We used various Reducer Nodes , simulation code and optimization algorithms in our experiments.
A summary is listed in Table~\ref{tab:built-in}
\begin{table*}
\centering
\begin{tabular}{p{4cm}|p{4cm}|p{4cm}}
\hline 
Reducer Node & simulator & optimization\\
\hline 
Geometry Node & optics & \multirow{4}{4cm}{Error diffusion, SPSA, Branch and bound}\\
 InputMesh, Stratum, Column&
 Reflectance and transmittance, caustics\\ \cline{1-2}
Material Node & deformation  \\
Constant, Layered,QuadLayer, SubdivisionSufrace& 
non-linear elasticity
\\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table*}
\subsection{Print Material Characterization and Measurement}
\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. 
In this example, we
tried to make the material as light as possible.
